Making Q-learning robust to time discretization

### 2019-01-17 paper/icml_drau/advup.tex

\subsection{Advantage Updating}
\label{subsec:reparam}
To define an object which contains the same information on actions as
$Q^\pi_\deltat$, but admits an action dependant continuous time limit, it is
natural to define
\begin{align}
	A^\pi_\deltat(s, a) &= \frac{Q^\pi_\deltat(s,a) - V^\pi_\deltat(s)}{\deltat},
    \label{eq:adv}
\end{align}
a rescaled version of the advantage function, as the difference between between
$Q^\pi_\deltat(s, a)$ and $V^\pi\deltat(s)$ is of order $\bigO(\deltat)$.
Contrary to the action state value function, the rescaled advantage function converges when $\deltat$ goes to $0$
to an action dependent quantity which contains the necessary information for policy improvement:

@@

\TODO{CT and LB are fighting each other about the importance which should be given to the next paragraph. A impartial judge should give his opinion. (CT is wrong)} However, the proposed reparameterization does not, on its own, guarantee that
when $Q$ correctly approximates $Q^\pi_\deltat$, $A$ approximates $A^\pi_\deltat$.
Indeed, for any given pair $V$, $A$,
\begin{align}
	\tilde{V}(s) &= V(s) - f(s)\\
	\tilde{A}(s, a) &= A(s, a) + \frac{f(s)}{\deltat}
\end{align}
yields the exact same $Q$ function. Consequently, $Q$ can correctly approximate
$Q^\pi$ even if $A$ is arbitrarily far from $A^\pi$.
To enforce, identifiability of $A$, one must enforce the consistency equation
\begin{equation}
	Q^\pi_\deltat(s, \pi(s)) - V^\pi_\deltat(s) = 0
\end{equation}
on the approximate $A$ and $V$. This translates to
\begin{equation}
	A(s, \pi(s)) = 0.
\end{equation}
With this additional constraint, if $Q^\pi_\deltat = Q$,
\begin{align}
	A^\pi_\deltat(s, a) &= \frac{Q^\pi_\deltat(s,a) - V^\pi_\deltat(s)}{\deltat}\\
		    &= \frac{Q(s,a) - Q(s, \pi(s))}{\deltat}\\
		    &= A(s, a).
\end{align}
In the spirit of~\cite{dueling_nets}, this condition is enforced by writing $A$ as
\begin{equation}
	A(s, a) = \bar{A}(s, a) - \bar{A}(s, \pi(s)).
\end{equation}
With this parameterization, one can hope to learn an approximation of $A^\pi_\deltat$,
from which a proper hiearchy of actions can be derived for any $\deltat$.

>>>>

\subsection{Advantage Updating}
\label{subsec:reparam}
To define an object which contains the same information on actions as
$Q^\pi_\deltat$, but admits an action dependant continuous time limit, it is
natural to define \cite{adv_upd}
\begin{align}
	A^\pi_\deltat(s, a) &= \frac{Q^\pi_\deltat(s,a) - V^\pi_\deltat(s)}{\deltat},
    \label{eq:adv}
\end{align}
a rescaled version of the advantage function, as the difference between between
$Q^\pi_\deltat(s, a)$ and $V^\pi\deltat(s)$ is of order $\bigO(\deltat)$.
Contrary to the action state value function, the rescaled advantage function converges when $\deltat$ goes to $0$
to an action dependent quantity which contains the necessary information for policy improvement:

@@

\TODO{CT and LB are fighting each other about the importance which should be given to the next paragraph. A impartial judge should give his opinion. (CT is wrong)} However, the proposed reparameterization does not, on its own, guarantee that
when $Q$ correctly approximates $Q^\pi_\deltat$, $A$ approximates $A^\pi_\deltat$.
Indeed, for any given pair $V$, $A$,
\begin{align}
	\tilde{V}(s) &= V(s) - f(s)\\
	\tilde{A}(s, a) &= A(s, a) + \frac{f(s)}{\deltat}
\end{align}
yields the exact same $Q$ function. Consequently, $Q$ can correctly approximate
$Q^\pi$ even if $A$ is arbitrarily far from $A^\pi$.
To enforce, identifiability of $A$, one must enforce the consistency equation
\begin{equation}
	Q^\pi_\deltat(s, \pi(s)) - V^\pi_\deltat(s) = 0
\end{equation}
on the approximate $A$ and $V$. This translates to
\begin{equation}
	A(s, \pi(s)) = 0.
\end{equation}
With this additional constraint, if $Q^\pi_\deltat = Q$,
\begin{align}
	A^\pi_\deltat(s, a) &= \frac{Q^\pi_\deltat(s,a) - V^\pi_\deltat(s)}{\deltat}\\
		    &= \frac{Q(s,a) - Q(s, \pi(s))}{\deltat}\\
		    &= A(s, a).
\end{align}
In the spirit of~\cite{dueling_nets}, this condition is enforced by writing $A$ as
\begin{equation}
\label{eq:Aparam}
	A(s, a) = \bar{A}(s, a) - \bar{A}(s, \pi(s)).
\end{equation}
With this parameterization, one can hope to learn an approximation of $A^\pi_\deltat$,
from which a proper hiearchy of actions can be derived for any $\deltat$.
